\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-15 manuscript.Rmd
Figure 5 Updates

# Proportion of off-diagonal elements >.10
sumR <- sum(BigRR/totRR*100)

@@

```{r EFAResiduals, out.height= "100%",  fig.align='center', fig.cap= ' Histogram of residuals:  five-factor solution',  out.width="100%",  warning=FALSE, results='asis'}
hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
abline(h =51, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)

>>>>

# Proportion of off-diagonal elements >.05
sumR <- sum(BigRR/totRR*100)

@@

```{r EFAResiduals, out.height= "100%",  fig.align='center', fig.cap= ' Histogram of residuals:  five-factor solution',  out.width="100%",  warning=FALSE, results='asis'}
hist(residual.5F,  main = NULL, xlab = "Residuals", ylim=c(0, 400))
abline(h =51, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)
